Finding Maximum $k$-Cliques Faster using Lazy Global Domination

### 2016-03-29 paper/paper.tex
Notation clash

A clique in a graph is a set of vertices, each of which is adjacent to every other vertex in the
set. Finding a clique of maximum size in a graph is one of the basic \NP-hard
problems \cite{Garey:1990}; applications include geometry, coding theory, computer vision and
bioinformatics \cite{Bomze:1999,Butenko:2006}. However, when analysing real-world data, a clique may
be too strong a requirement. A $k$-clique (or sometimes $n$-clique or $s$-clique) is a relaxed form
of clique, where instead of requiring each pair of vertices to be directly adjacent, we only require
that they be connected by a path of length at most $k$ \cite{Luce:1950}. Thus a $1$-clique \emph{is} a
clique, a $2$-clique may be thought of as ``a group of people, all of whom either know each other or
have a mutual acquaintance'', and so on. We illustrate this in \cref{figure:k-cliques}.
Determining the size of a maximum $k$-clique is \NP-hard for any fixed $k$ \cite{Bourjolly:2002}.

>>>>

A clique in a graph is a set of vertices, each of which is adjacent to every other vertex in the
set. Finding a clique of maximum size in a graph is one of the basic \NP-hard problems
\cite{Garey:1990}; applications include geometry, coding theory, computer vision and bioinformatics
\cite{Bomze:1999,Butenko:2006}. However, when analysing real-world data, a clique may be too strong
a requirement. A $k$-clique (or sometimes $n$-clique or $s$-clique) is a relaxed form of clique,
where instead of requiring each pair of vertices to be directly adjacent, we only require that they
be connected by a path of length at most $k$ \cite{Luce:1950} \footnote{In an unfortunate clash of
notation, the name ``$k$-clique problem'' is sometimes used elsewhere to refer the decision version
of the clique problem, to distinguish it from the maximum clique problem.}.  Thus a $1$-clique
\emph{is} a clique, a $2$-clique may be thought of as ``a group of people, all of whom either know
each other or have a mutual acquaintance'', and so on. We illustrate this in
\cref{figure:k-cliques}.  Determining the size of a maximum $k$-clique is \NP-hard for any fixed $k$
\cite{Bourjolly:2002}.
